Mitigating DDoS attacks in Named Data Networking

### 2012-12-01 ddos-ndn.tex
ddos attacks in ndn
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@840 df1a90cd-247b-4364-bdaf-287a704eb499

\section { DDoS Attacks in NDN \label{ddos-ndn}}
Brief overview of possible attacks in NDN, and scope of what we will tackle in this paper (Interest flooding).

%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
%  \caption{Strength of Interest flooding attack}
%  \label{fig:simemupower}
%\end{figure}

>>>>

\section { DDoS Attacks in NDN \label{ddos-ndn}}
Any DoS attack aims to exhaust system resources. In the context of NDN by term "system" we understand two things: 1) every individual NDN router 2) a distributed system consisting of some collection of NDN routers. In a first case, every major data structure (FIB, CS, PIT) is a potential surface for denial of service attack. In a second case, we consider: 1) bandwidth between NDN routers 2) caching capabilities of NDN routers 3) packet processing capabilities of NDN routers.

Let's examine an individual NDN router first. Certainly, as any other piece of software each specific NDN implementation can have bugs and exploits e.g. buffer overflows leading to data corruption in cache, etc. In this paper we are assuming an idealized NDN implementation lacking any implementation bugs.

In a general case, Forwarding Interest Base (FIB) is managed by routing protocol and if attackers have been able to get control over routing, they could advertise a huge number of FIB announcements that will fill up FIB table that may cause Interest processing delays and traffic redirection with amplification or black-holing.

Pending Interest Table (PIT) is used to keep per packet forwarding state in NDN and is critical for Data delivery. Though PIT table has an upper limit on its size, it doesn't prevent attacker from injecting a huge number of false Interest packets at a very high rate, which eventually will lead to a situation where the whole PIT table is full of false Interest packets and is not able to keep forwarding state of Interests coming from legitimate users. This attack may look similar to TCP SYN-flood attack and we call it Interest flooding.

Content Store (CS) is an effective obstacle for several types of DDoS attacks. CS possesses two important characteristics: maximum size and replacement policy. However, by knowing replacement policy attacker can construct a specific traffic generator that is using weaknesses of a chosen replacement procedure that will lead to increased processing time, slower packet delivery and in some cases de facto a complete inability to cache legitimate data.

An infrastructure consisting of NDN routers is vulnerable to the following types of attacks: 
\begin{enumerate}
\item Interest flooding. 
\item fkjgkfjgkfg
\end{enumerate} 
%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
%  \caption{Strength of Interest flooding attack}
%  \label{fig:simemupower}
%\end{figure}

### 2012-12-01 intro.tex
ddos attacks in ndn
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@840 df1a90cd-247b-4364-bdaf-287a704eb499

We believe that future Internet architectures can do and must do more for DDoS prevention.

\todo{
Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.

Our contributions.

Paper organization.}

In this paper we analyze all aspects of Interest flooding attack in NDN architecture, propose multiple defensive techniques against such kind of attacks, establish evaluation methodology using ndnSIM simulation software, execute small scale and Internet scale attack scenarios, and analyze our experimental results.

>>>>

IP architecture has a wide surface for denial of service attacks which takes the beginning from the thin-waist IP protocol, goes through transport level and up to DNS level. In IP it is very easy to forge source address and specify the exact destination that needs to be placed under attack that creates possibilities to perform various types of reflection DoS attacks. On transport level in TCP/IP SYN flood, RST flood and FIN-way attacks are very effective and popular. DNS system can be attacked in multiple ways, e.g. DNS amplification attack.

We believe that future Internet architectures can do and must do more for DDoS prevention. By its design NDN architecture is not sensitive to any kind of reflection attacks due to the lack of host addresses and ubiquitous data caching. NDN architecture can operate without any DNS-like architecture since it routes and forwards packets based on human-readable names instead of IP addresses that need to be resolved with DNS.

%\todo{
%Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.

%Our contributions.

%Paper organization.}

In this paper we provide a brief overview of possible DDoS attacks in NDN architecture, analyze all aspects of Interest flooding attack in NDN architecture, propose multiple defensive techniques against such attacks, establish evaluation methodology using ndnSIM simulation software, execute small scale and Internet scale attack scenarios, and analyze our experimental results.
